---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fudukue (文机)

`fukudue` is a collection of R packages developed to support literate programming with R mainly for the author.
This package will be used in conjunction with [`tidyverse`](), [`knitr`]() and [`bookdown`]().


## Installation

You can install:

* the latest development version from github with

```R
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/fudukue")
```


## How to use

### functions for routine operations

following functions are automatically globalized when this package is attached.

* `length2`, `sum2`, `sd2`, `mean2`
    * `na.rm = T` versions

* `se`
    * calculates a non-biased standard error
    
* `%!in%` (binary operator)
    * `a %!in% b` returns `!(a %in% b)`


### consistent cross-references displayed in .pfd and .docx

- [demo](https://github.com/KeachMurakami/fudukue/tree/master/demo/cross-reference)

`fudukue` implements the following verbs for generating consistent cross-reference both in .pdf and .docx (described in reference_switch.R).

* `initialize_ref()`
    * setups lookup table.

* `update_ref()`
    * adds id to newly called object.

* `ref_eqn(), ref_fig(), ref_table()`
    * generate continuous numbering from the given id.



### citation managements

`fudukue` implements the following verbs for updating bibtex-style references.
`.bib` files for respective articles are stored as `bibtex/list_bib/***.bib`

* `update_cite()`
    * calls `update_abbrv()` and `update_bib()`.

* `update_abbrv()`
    * loads abbreviation lists (.csv) and generates `abbrev_XXX.bib` files required for `update_bib()`.

* `update_bib()`
    * merges all bibtex files into three files.
        - `Full.bib`: **non-abbreviated** full-length titles
        - `With.bib`: abbreviated titles **with periods**
        - `Without.bib`: abbreviated titles **without periods**


## Session information

```{r sessioninfo}
devtools::session_info()
```
