---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fudukue (文机)

`fukudue` is a R package developed to support literate programming with R mainly for the author.
This package will be used in conjunction with [`knitr`]() and [`bookdown`]().


## Installation

You can install:

* the latest development version from github with

```R
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/fudukue")
```


## How to use

### consistent cross-references displayed in .pfd and .docx

- [demo](https://github.com/KeachMurakami/fudukue/tree/master/demo/cross-reference)

`fudukue` implements the following verbs for generate consistent cross-reference both in .pdf and .docx (described in reference_switch.R).

* `initialize_ref()`
    * setup lookup table

* `update_ref()`
    * add id to newly called object.

* `ref_eqn(), ref_fig(), ref_table()`
    * generate continuous numbering from the given id.

```{r demo_crossref}
library(fudukue)
library(tidyverse)

initialize_ref(list_name = "fig", max_object_num = 5)

# fig 1
plot(1:10)

update_ref(id = "one2ten", list_name = "fig")

# fig 2
hist(rnorm(200, 0, 1))

update_ref(id = "hist", list_name = "fig")


# for latex output
out_type <- "latex"
ref_fig(id = "hist", prefix = "Fig. ")

# for docx output
out_type <- "docx"
ref_fig(id = "hist", prefix = "Fig. ")
```


## Session information

```{r sessioninfo}
devtools::session_info()
```
