---
title: "demo_crossref"
output:
  bookdown::word_document2:
    toc: FALSE
  pdf_document:
    toc: FALSE
---

```{r load}
library(knitr)
library(tidyverse)
library(fudukue)

out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")

initialize_ref(list_name = "fig", max_object_num = 5)
initialize_ref(list_name = "eqn", max_object_num = 5)
```

# Analyses section

\begin{equation}
  f(x) = \dfrac{1}{\sqrt{2 \pi \sigma^2}}\exp({- \dfrac{(x - \mu)^2}{2 \sigma^2}})
  `r if(out_type == "latex") "%"` (\#eq:eqn1)
  `r if(out_type == "docx") "%"` \label{eq:eqn1}
\end{equation}

`r update_ref(id = "normal_dist", list_name = "eqn")`


```{r fig1, fig.cap = "\\label{fig:plot}Normally distributed values."}
n01 <- rnorm(100, 0, 1)

plot(n01)
```

`r update_ref(id = "plot", list_name = "fig")`

```{r fig2, fig.cap = "\\label{fig:hist}Histogram of normally distributed values."}
hist(n01)
```

`r update_ref(id = "hist", list_name = "fig")`


# Reporting section

- An equation can be cited in the manuscript as follows:

`r ref_eqn(id = "normal_dist", prefix = "Eqn. ")` shows the probability density of the normal distribution.

- A figure can be cited in the manuscript as follows:

`r ref_fig(id = "plot", prefix = "Fig. ")` shows normally distributed 100 values, and `r ref_fig(id = "hist", prefix = "Fig. ")` is a histogram of them.
One can cite plural figures by `r ref_fig(id = c("plot", "hist"), prefix = "Figs. ")`.


```{r, eval = FALSE}
rmarkdown::render(input = "demo/cross-reference/demo_crossref.Rmd", "all")
```
